Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-11 Chapter-1/1-Theory.tex
s

The key elements of a neutrino event generators for resonance and DIS events are the nuclear model and the hadron treatment (both production and transportation). As one of the most popular event generators for LAr experiments, we take GENIE~\cite{Andreopoulos:2009rq} here as an example.
The nuclear model used by GENIE for all processes is a relativistic Fermi gas (RFG) modified to incorporate short range nucleon-nucleon correlations \cite{PhysRevD.24.1400}. This means that the initial momentum and binding energy of the struck nucleon is determined by assuming nucleons inside the nucleus are quasi-free, acting independently in the mean field of the nucleus. For A $ >$ 20 like argon, the 2-parameter Woods-Saxon shell model for density function is used.  The GENIE module INTRANUKE \cite{Juszczak2006} is used to simulate the final-state interactions (FSI) which is the hadron re-interaction inside the nucleus. This module places the outgoing particles in the nucleus and propagates them.  In the INRANUKE model, hadrons cannot undergo more than one FSI per event. When possible, external hadron-nucleus scattering data are used to tune INTRANUKE. Since no data is available for Argon, GENIE uses an interpolation of data from heavier and lighter nuclei for the pion-argon cross section leading to big uncertainties in the INTRANUKE module.

@@

\textcolor{red}{explain geant4 }
\textcolor{red}{explain Genie }
Figure \ref{fig:PionTrueArgon} shows the Geant4 prediction for the total, elastic and reaction cross section for $\pi^-$ on argon.

>>>>

The key elements of a neutrino event generators for resonance and DIS events are the nuclear model and the hadron treatment (both production and transportation). As one of the most popular event generators for LAr experiments, we take GENIE~\cite{Andreopoulos:2009rq} here as an example.
The nuclear model used by GENIE for all processes is a relativistic Fermi gas (RFG) modified to incorporate short range nucleon-nucleon correlations \cite{PhysRevD.24.1400}. This means that the initial momentum and binding energy of the struck nucleon is determined by assuming nucleons inside the nucleus are quasi-free, acting independently in the mean field of the nucleus. For A $ >$ 20 like argon, the 2-parameter Woods-Saxon shell model for density function is used.  The GENIE module INTRANUKE \cite{Juszczak2006} is used to simulate the final-state interactions (FSI) which is the hadron re-interaction inside the nucleus. This module places the outgoing particles in the nucleus and propagates them using the ``hA model".  In the INRANUKE hA model, hadrons can undergo at most one FSI per event. When possible, external hadron-nucleus scattering data are used to tune INTRANUKE. Since no data is available for Argon, GENIE uses an interpolation of data from heavier and lighter nuclei for the pion-argon cross section leading to big uncertainties in the INTRANUKE module.

@@

LArIAT uses Geant4 as the default simulation package. In particular, pions (and kaons) transportation is achieved through the Geant4 FTFP\_BERT physics list. In this physics list, Geant4 uses the Bertini cascade model  \cite{Wright:2015xia}  to simulate the products of the pion-nucleus interaction as well as the hadrons re-interactions inside the target nucleus (intra-nuclear cascade).  REWRITE THE FOLLOWING
%The target nucleus is treated as an average nuclear medium, in which the nucleons are assumed to have a Fermi gas momentum distribution. The final state of each collision is sampled according to free-particle cross section data. Clusters of nucleons are considered only in case of pion absorption which requires at least dinucleons. Nuclear effects, i.e. secondaries which can interact with other protons and neutrons inside the nucleus and so on until the last secondaries es-cape the nucleus or are absorbed, are also taken in account. This model reproduces detailed cross section data for nucleons, pions and kaons in the region below 1 GeV and is expected to do reasonably well in the multi-GeV region.

%Genie
The relevance of the GENIE generator for neutrino physics and its basic working principles have been outlined earlier in this section. Information on hadron-nucleus interactions can be extracted from the  INTRANUKE module and compared against the Geant4 predictions, as shown in Figure    \ref{fig:pionCa}.
%Calcium explained
%Carbon explained

Figure \ref{fig:PionTrueArgon} shows the Geant4 prediction for the total, elastic and reaction cross section for $\pi^-$ on argon.
